Barneby Lives!

### 2023-07-06 scripts/taxonomy_setup.Rmd
refining tutorial

sppLKPtab <- cla[, c('scientificName', 'specificEpithet', 'infraspecificEpithet', 'verbatimTaxonRank')]
sppLKPtab <- filter(sppLKPtab, is.na(verbatimTaxonRank) | verbatimTaxonRank != "f.")

>>>>

sppLKPtab <- cla[, c('scientificName', 'specificEpithet', 'infraspecificEpithet', 'verbatimTaxonRank')]
sppLKPtab <- filter(sppLKPtab, is.na(verbatimTaxonRank) | verbatimTaxonRank != "f.") %>% 
  mutate(Grp = str_extract(specificEpithet, '[a-z]{3}'))
